---
title: "GeneralAnalysis"
format: 
  html:
    code-fold: true
    code-tools: true
---

## About the data

The dataset, scraped from [Nemesis](http://nemesis555nchzn2dogee6mlc7xxgeeshqirmh3yzn4lo5cnd4s5a4yd.onion/) between 1^st^ January to 11^th^ January, contains 1334 files comprising 607 posts on drug sales, 415 posts on fraud, 134 posts providing guides and tutorials on illegal activities, and other miscellaneous posts. In this analysis, we will focus solely on the drug sales-related posts.

As the original documents were in text format, which made it difficult to carry out quantitative analysis, I cleaned the data and put them into a data frame. I then saved the data frame as a CSV file named "complete.csv".

## The payment method

**Bitcoin and Monero accepted.** All items are listed as an **escrow**. The order process is as follows:

-   After the buyer has placed an order, the vendor has 5 days to accept or reject the order.
-   The buyer will get a full refund if the vendor doesn't accept the order within 5 days.
-   If the buyer doesn't want to wait 5 days, there will be a cancel button after 48 hours to cancel the order and get a full refund.
-   After the order got accepted, the vendor has 5 days to send it. The buyer can not cancel the order at this point.
-   The buyer will get a full refund if the vendor doesn't send the order within 5 days.
-   The buyer has 3 days to open a dispute if the order does not match the description.
-   After the order got finalized, the buyer can leave a review.
-   If you have any questions, leave a comment or create a post on our forum.

## Load Packages and data

```{r}
#| label: load-packages_data
#| warning: false
#| code-fold: true

library(tidyverse)
library(forcats)
library(stringr)
library(tidytext)
library(igraph)
library(ggraph)
library(ggrepel)


data  <-  read_csv("/Users/shihaitao/Documents/DarknetProject/Nemesis/complete.csv")
```

## The number of posts of each type of drugs (Top20)

```{r}
#| warning: false
data %>% 
  group_by(Drug_Type) %>% 
  summarise(count = n()) %>% 
  tidyr::separate(Drug_Type, into = c("Drug_Type", "Drug_Sub"), sep = "  » ") %>%
  arrange(desc(count)) %>% 
  head(.,20)
```

## The number of posts of each drug (Top20)

```{r}
#capitalise all the drug names and count 
data$DrugName <- toupper(data$DrugName)
item_counts <- data %>% group_by(DrugName) %>% summarise(count = n()) %>% arrange(desc(count))
head(item_counts, 20)
```

## The brand name of the drugs for sale

The table below shows each brand name and its number of occurrences, and it can be observed that MONSTERLAB and HYDROGURU are the brands with the highest number of occurrences. These two brands are not specific to any particular drug, but rather the names of the dealers. It seems that they have generated a certain brand effect, representing a guarantee of high-quality drugs.

```{r}
data$BrandName <- toupper(data$BrandName) 
BrandName_Re_NA <- data$BrandName[!is.na(data$BrandName)] #remove NA
brand_counts <- as_tibble(table(BrandName_Re_NA))
colnames(brand_counts) <- c("BrandName", "Count")
brand_counts <- brand_counts %>% arrange(desc(Count))
brand_counts
```

### The brand name of XTC Pills

Another interesting observation is that the brand name of XTC Pills may indicate the strength or purity of these drugs and also provide a guarantee of quality for buyers. This requires further qualitative analysis and exploration.

```{r}
data %>% filter(Drug_Type == "Ecstasy  » XTC Pills"& !is.na(BrandName)) %>% select(Drug_Type, BrandName) %>% unique() 
```

### The avalibility rate

```{r}
mean(data$Availablity == "Yes", na.rm = TRUE)
```

## Rating, Reviews and Sales

```{r}
#Get the Rating number from strings
data$Rating <- data$Rating %>% 
  str_extract("\\d+(\\.\\d+)?") %>% 
  as.numeric()
#Select the columns that we need
data_RRS <- data %>% select(DrugName,Drug_Type,Vendor_Name, Rating,Reviews,Sales)
```

### Let's see what the header of the new DataFrame looks like and the statistical information about ratings, reviews, and sales.

```{r}
head(data_RRS)
summary(data_RRS[, c("Rating", "Reviews", "Sales")])
```

### Grouped summary statistics: Calculate summary statistics for each type of drug.

```{r}
group_Drug_Type <- data_RRS %>%
  group_by(Drug_Type) %>%
  summarise(mean_rating = mean(Rating),
            total_reviews = sum(Reviews),
            toal_sales = sum(Sales))
```

**Best-selling drug types (top 20)**

```{r}
group_Drug_Type %>% 
arrange(desc(toal_sales)) %>% head(20)%>% select(Drug_Type,toal_sales)
```

**Highest rated drug types (top 20)**

```{r}
group_Drug_Type %>% 
arrange(desc(mean_rating)) %>% head(20) %>% select(Drug_Type, mean_rating)
```

**Types of drugs that get the most views (top 20)**

```{r}
group_Drug_Type %>% 
arrange(desc(total_reviews)) %>% head(20) %>% select(Drug_Type, total_reviews)
```

### Grouped summary statistics: Calculate summary statistics for Vendors.

```{r}
group_Vendor <- data_RRS %>%
  group_by(Vendor_Name) %>%
  summarise(mean_rating = mean(Rating),
            total_reviews = sum(Reviews),
            total_sales = sum(Sales))
group_Vendor
```

**Top 10 vendors based on sales**

```{r}
group_Vendor %>% 
  arrange(desc(total_sales)) %>% 
  select(Vendor_Name,total_sales) %>% 
  head(10)

```

**Bottom 10 vendors based on sales**

```{r}
group_Vendor %>% 
  arrange(desc(total_sales)) %>% 
  select(Vendor_Name,total_sales) %>% 
  tail(10)
```

By comparing sales figures, we can identify who the top sellers are on this platform, as well as who the newcomers or less established sellers might be. We can further examine their advertising, returns policies, and self-introductions to understand why some sellers' products are more popular and in what ways they gain the trust of buyers.

```{r}

```

## Limitations

The sample size of the data is small. The time span for collecting the data is quite extensive (i.e., 11 days). During these days, trading did not cease and the data such as rating, the number of sale and reviews will change, which may introduce inaccuracies into the statistics.
