---
title: "GeneralAnalysis"
format: 
  html:
    code-fold: false
    code-tools: true
---

## About the data

The dataset, scraped from [Nemesis](http://nemesis555nchzn2dogee6mlc7xxgeeshqirmh3yzn4lo5cnd4s5a4yd.onion/) between 1^st^ January to 11^th^ January, contains 1334 files comprising 607 posts on drug sales, 415 posts on fraud, 134 posts providing guides and tutorials on illegal activities, and other miscellaneous posts. In this analysis, we will focus solely on the drug sales-related posts.

As the original documents were in text format, which made it difficult to carry out quantitative analysis, I cleaned the data and put them into a data frame. I then saved the data frame as a CSV file named "complete.csv".

## The payment method

**Bitcoin and Monero accepted.** All items are listed as an **escrow**. The order process is as follows:

-   After the buyer has placed an order, the vendor has 5 days to accept or reject the order.
-   The buyer will get a full refund if the vendor doesn't accept the order within 5 days.
-   If the buyer doesn't want to wait 5 days, there will be a cancel button after 48 hours to cancel the order and get a full refund.
-   After the order got accepted, the vendor has 5 days to send it. The buyer can not cancel the order at this point.
-   The buyer will get a full refund if the vendor doesn't send the order within 5 days.
-   The buyer has 3 days to open a dispute if the order does not match the description.
-   After the order got finalized, the buyer can leave a review.
-   If you have any questions, leave a comment or create a post on our forum.

## Load Packages and data

```{r}
#| label: load-packages_data
#| warning: false
#| code-fold: true

library(tidyverse)
library(forcats)
library(stringr)
library(tidytext)
library(igraph)
library(ggraph)
library(ggrepel)
library(car)
library(geosphere)
library(countrycode)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(lwgeom)
library(ggsankey)
library(networkD3)



data  <-  read_csv("/Users/shihaitao/Documents/DarknetProject/Nemesis/complete.csv")
```

## The number of posts of each type of drugs (Top20)

```{r}
#| warning: false
data %>% 
  group_by(Drug_Type) %>% 
  summarise(count = n()) %>% 
  tidyr::separate(Drug_Type, into = c("Drug_Type", "Drug_Sub"), sep = "  » ") %>%
  arrange(desc(count)) %>% 
  head(.,20)
```

Different types of drug are sold in Nemesis, namely, Cannabis, Dissociatives, Opioids, Steroids, Psychedelics, Stimulants, Prescription Drugs, Benzodiazepine (Benzos), Ecstasy, and others. Some drug type has specific subcategories associated with it. For example, under the drug type Cannabis, the subcategories include Buds and Flowers, Hash, and Shake. The "count" column represents the number of posts for each drug subcategory, indicating the frequency or popularity of each drug subcategory. For instance, the drug subcategory "Buds and Flowers" has a count of 103, and it has the highest number of posts among all the drug subcategories listed. Dissociatives (Ketamine), Ecstasy (XTC Pills), Steroids, and Stimulants (Cocaine, Amphetamine/Speed) also have significant counts, suggesting their popularity in the market.

## The number of posts of each drug (Top20)

```{r}
#capitalise all the drug names and count 
data$DrugName <- toupper(data$DrugName)
item_counts <- data %>% group_by(DrugName) %>% summarise(count = n()) %>% arrange(desc(count))
head(item_counts, 20)
```

The data frame consists of the top 20 drug names mentioned in posts. The "count" column represents the number of posts for each drug. It can partly indicate the popularity of each drug. Based on the counts, we can see that LSD (n=14), Heroin (n=9), Gorilla Glue (n=7), Racemic Ketamine (n=7), and Xanax (n=7) have relatively higher counts, suggesting a higher level of discussion or interest in these drugs.

## The brand name of the drugs for sale

The table below shows each brand name and its number of occurrences, and it can be observed that MONSTERLAB and HYDROGURU are the brands with the highest number of occurrences. These two brands are not specific to any particular drug, but rather the names of the dealers. It seems that they have generated a certain brand effect, representing a guarantee of high-quality drugs.

```{r}
data$BrandName <- toupper(data$BrandName) 
BrandName_Re_NA <- data$BrandName[!is.na(data$BrandName)] #remove NA
brand_counts <- as_tibble(table(BrandName_Re_NA))
colnames(brand_counts) <- c("BrandName", "Count")
brand_counts <- brand_counts %>% arrange(desc(Count))
brand_counts
```

### The brand name of XTC Pills

Another interesting observation is that the brand name of XTC Pills may indicate the strength or purity of these drugs and also provide a guarantee of quality for buyers. For instance, ORANGE TESLA with the warning "strong, be careful!" (01025.txt) may harbour more potential strength compared to Pink Glitter Tesla, with the description "very clean and stimulating" (00307.txt). While almost all vendors selling XTC Pills highlight the "high quality" of their products, some emphasise that their XTC Pills have been "lab tested" (13 out of 42 posts) or "black light tested and reagent tested with Marquis and Froehd" (00458 and 01025). Such measures in place serve the primary role of ensuring top-notch quality and utmost safety.

```{r}
data %>% filter(Drug_Type == "Ecstasy  » XTC Pills"& !is.na(BrandName)) %>% 
  select(Drug_Type, BrandName) %>% 
  unique() 
```

```{r}
#| echo: FALSE
#see the description of XTC Pills
#view(data %>% filter(Drug_Type =="Ecstasy  » XTC Pills") %>% select(File_Name,BrandName,MainContent)) 
```

### The availibility rate

```{r}
mean(data$Availablity == "Yes", na.rm = TRUE)
```

It is worth mentioning that not all drugs available on the market are actually available on Nemesis Market. According to the dataset provided, the availability rate of drugs on the Nemesis Market is 95.87%. This may be due to reasons such as the drug being sold out or the drug vendors being on holiday.

## Rating, Reviews and Sales

```{r}
#Get the Rating number from strings
data$Rating <- data$Rating %>% 
  str_extract("\\d+(\\.\\d+)?") %>% 
  as.numeric()
#Select the columns that we need
data_RRS <- data %>% select(DrugName,Drug_Type,Vendor_Name, Rating,Reviews,Sales)
data_RRS %>% filter(Sales==0)
```

127 drugs have never been sold, so it would be better to remove them before analysing the data.

```{r}
data_RRS_noZero <- data_RRS %>% filter(Sales!=0)
```

### Let's see the statistical information about ratings, reviews, and sales.

```{r}
summary(data_RRS_noZero[, c("Rating", "Reviews", "Sales")])
```

### Grouped summary statistics: Calculate summary statistics for each type of drug.

```{r}
group_Drug_Type <- data_RRS_noZero %>%
  group_by(Drug_Type) %>%
  summarise(mean_rating = mean(Rating),
            total_reviews = sum(Reviews),
            toal_sales = sum(Sales))
```

**Best-selling drug types (top 20)**

```{r}
group_Drug_Type %>% 
arrange(desc(toal_sales)) %>% head(20)%>% select(Drug_Type,toal_sales)
```

**Highest rated drug types (top 20)**

```{r}
group_Drug_Type %>% 
arrange(desc(mean_rating)) %>% head(20) %>% select(Drug_Type, mean_rating)
```

**Types of drugs that get the most reviews (top 20)**

```{r}
group_Drug_Type %>% 
arrange(desc(total_reviews)) %>% head(20) %>% select(Drug_Type, total_reviews)
```

### Grouped summary statistics: Calculate summary statistics for Vendors.

```{r}
group_Vendor <- data_RRS_noZero %>%
  group_by(Vendor_Name) %>%
  summarise(total_reviews = sum(Reviews),
            total_sales = sum(Sales))
```

**Top 10 vendors based on sales**

```{r}
group_Vendor %>% 
  arrange(desc(total_sales)) %>% 
  select(Vendor_Name,total_sales) %>% 
  head(10)

```

**Bottom 10 vendors (excluding those who never sold anything) based on sales**

```{r}
group_Vendor %>% 
  arrange(desc(total_sales)) %>% 
  select(Vendor_Name,total_sales) %>% 
  tail(10)
```

By comparing sales figures, we can identify that the top 10 sellers are SocialPharma (103577), maurelius(101537), MicroDroper(65912), queenofcannabis(58002), PingPongUK(44556), discover(44148), DrRelax(40992), TorDrug(39424), drugstar(36168), and straightfromnl(35666). The numbers in the parenthesis are sales on this platform. On the other hand, yodiweed(5), BSPLLC(3), kings(3), shinyflakes(3), OliverTwiztt(2), POPEYE_GERMANY(2), DoctorPotenz(1), Grüneapotheke(1), Replicagod(1), UKnarcotics(1) are the newcomers or less established sellers.

We can further examine their advertising, returns policies, and self-introductions to understand why some sellers' products are more popular and in what ways they gain the trust of buyers.

```{r}
View(data %>% filter(Vendor_Name=="SocialPharma") %>% select(File_Name, Drug_Type, MainContent,Refund,Review))
```

The highest-selling vendor is called SocialPharma (filename: 00132, 00373, 00483, 00519, 00520, 00721, 00923, 01107), and they primarily sell two types of drugs, namely Benzodiazepine (Benzos) and Opioids. Only Oxycodone is shipped from the United Kingdom to worldwide destinations, and it is marked as "non-refundable/non-reshipable." The other products he sells, namely Zopiclone, Diazepam (Valium), Dihydrocodeine, Codeine, and Tramadol, are sold locally in the UK and have corresponding return and exchange policies. The vendor is a self-employed because he always refers to himself with "me" instead of "us".

Surprisingly, his drug descriptions are often limited to just two lines, specifying the quantity and strength, without mentioning the quality of the products. Similarly, his return and exchange policies are quite brief. He offers either a reshipment or a 50% refund based on the buyer's purchase time and his own perception of the buyer's trustworthiness.

Therefore, we can assume that the trust generated by the high ratings (all five stars) and a large number of reviews no longer requires him to go through the trouble of describing the product and building trust. In a way, the rating system and sales data have established trust that surpasses the need for product descriptions themselves. Another explanation could be attributed to the types of drugs they sell. Most of these drugs are sold in tablets, which gives limited room for detailed descriptions. This is in stark contrast to vendors selling Cannabis.

```{r}
View(data %>% filter(Vendor_Name=="maurelius") %>% select(File_Name, Drug_Type, MainContent,Refund,Review))
```

The second-largest vendor in terms of sales is named Maurelius (Filenames: 00028, 00137, 00497, 00498, 00544, 00550, 00553, 00554, 01168, 01170, 01206, 01227, 01240, 01249, 01250, 01253). They specialize in selling Cannabis (Shake, Hash, and Buds and Flowers) with detailed descriptions. **Tetrahydrocannabinol (THC)** level is generally provided as an indicator for potency. Numerous paragraphs are dedicated to describing the aroma and taste of each Cannabis product. For example, when describing Afghan Kush, the aroma and taste of this strain are mentioned three times.

> The aroma of this medical marijuana strain will be like a mango orange farm with a pinch of funky odor. The taste of this strain is not at all harsh. This will have a bland and fruity taste. (01253, Pos. 35-37)

> Flavors\
> Herbal, Pine, Spicy, Sweet, Woody\
> Aromas\
> Earthy, Floral, Kush, Pungent, Spicy, Sweet (01253, Pos. 47-50)

> Aroma
>
> As is the case with pretty much every single strain from the Hindu Kush mountain range, the primary aroma of the Afghan Kush strain is one of hash.
>
> Dense, powdery, and just a little bit spicy, this strain smells like walking into a familiar and friendly hash pipe shop in the Middle East or West India.
>
> There is sweetness there, but the overwhelming characteristic of the aroma is one of dankness and pleasant hash.
>
> Flavor
>
> The overwhelming quality of the taste of the Afghan Kush smoke is one of sweet hash. It is pretty similar to its aroma, though, with a few key differences that help set it apart.
>
> Instead of the intense spiciness that you'd expect after walking nearby any Afghan Kush bud, the leading quality is one of dank hash. As soon as it hits your tongue, you feel almost overpowered by the taste of hashish.
>
> In a way, Afghan Kush tastes like a real marijuana experience -- that quintessential flavor quality that makes smoking marijuana what it is. (01253, Pos. 85-100)

Furthermore, the heritage/hybrid of Cannabis is also an important aspect that vendors want to emphasise to highlight the rarity and effects of their products. For example:

> Alien Cookies is an evenly balanced hybrid (50% sativa/50% indica) strain created through a cross of the popular Alien Dawg X Girl Scout Cookies strains. This bud is incredibly rare to find, but totally worth it every time because of its flawless combination of its parents' effects. (01240, Pos. 27-30)

The effects of different drugs on the body reveals several patterns:

1.  Social Behavior and Creativity: Individuals who seek these drugs for their psychotropic effects may seek to experience heightened sociability, amplified ethusiasm and to facilitate creative endeavors.
2.  Euphoria and Blissful Sensations: These effects may contribute to a sense of happiness, cheerfulness, and laughter, thereby attracting individuals seeking positive emotional experiences.
3.  Relaxation and Body Buzz: This combination of physical relaxation and elevated mood may be appealing to individuals seeking stress relief, tranquility, and a soothing experience.
4.  Medicinal Benefits: Individuals may turn to these drugs for potential therapeutic effects.
5.  Sleep and Sedation: Some individuals may seek these drugs to aid with sleep-related issues or relaxation before bedtime.

**Ways to attract purchase or gain trust:**

1.  Being frankly about the side effects: while dry mouth and dry eyes are often mentioned in the posts, medical adverse reactions are listed. For example,

    > ADVERSE REACTIONS: Dry mouth, Dry eyes\
    > MEDICAL Depression, Insomnia, Stress, Cramps, Fatigue (00498, Pos. 59-60)

    用过By providing honest and transparent information about the side effects and dangers of drugs, vendors can, to some extent, build trust. Potential users may be more inclined to work with vendors who are concerned about user safety. Vendors may feel that they have an ethical responsibility to provide accurate information to potential users to ensure that users are able to make informed decisions.

2.  The minimal negative side effects: for example, the vendor points out that Amnesia Haze is a sativa strain with minimal negative side effects compared to other sativa strains, as it doesn't induce dizziness, paranoia, anxiety, or nausea. The main drawback of Amnesia Haze is dry mouth (cotton mouth), which can be alleviated by staying hydrated before, during, and after cannabis consumption. (see 00497, Pos. 92-101)

> Refund Policy: "If your order doesn't show up we can offer you 50% reship or refund of the original order. For years we used to reship 100% of the orders but unfortunately we live in a world where people take advantage of you and sometimes our clients lie when it comes to receiving orders. Please understand that we are here for money and we feel sorry that honnest men/women have to suffer the loss. Besides, you are buying weed, not vegetables. :)"

In the refund policy, it was mentioned that 100% of orders would be reshipped in the past, but later it was changed to only providing 50% reshipment or refund. This indicates that there have been changes in the market dynamics. Customers who receive the items can still lie and claim that they have not received them in order to deceive for a refund or reshipment. Sellers are increasingly experiencing such negative experiences, which forces them to adjust their return and exchange policies to ensure overall profitability. This return and exchange policy reflects that the trust between sellers and buyers has not been resolved by the escrow method. The sale of drugs is not regulated or protected by law, and buyers and sellers seek a balance of trust through interaction and experience. This is further evidenced by the refund policy provided by SocialPharma, which is based on his perception of the buyer's trustworthiness.

```{r}
#| echo: false
View(data %>% filter(Vendor_Name=="MicroDroper") %>% select(File_Name, Drug_Type, MainContent,Refund,Review))
```

销量第三的vendor是以MicroDroper的昵称进行销售的，这是一个专业售卖ISOTONITAZENE\
和Fentanyl的team,

### Bar plot of average rating per Drug_Type:

```{r}
data_RRS_noZero %>%
  group_by(Drug_Type) %>%
  summarise(mean_rating = mean(Rating)) %>%
  arrange(mean_rating) %>%
  ggplot(aes(x = reorder(Drug_Type, mean_rating), y = mean_rating, fill = Drug_Type)) +
  geom_bar(stat = "identity") +
  geom_text(aes(x = reorder(Drug_Type, mean_rating), y = mean_rating, label = round(mean_rating, 2)), vjust = 0.6, hjust=0,size = 2) + 
  # Add geom_text to display value labels
  theme_minimal() +
  labs(title = "Average Rating per Drug Type", y = "Average Rating", x = "Drug Type") +
  theme(legend.position = "none", axis.text.y = element_text(size = 8)) +
  coord_flip()
```

### Scatter plot of Sales vs. Review

```{r}
ggplot(data_RRS_noZero, aes(x = Reviews, y = Sales)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Sales vs. Reviews", x = "Reviews", y = "Sales") +
  geom_smooth(method = "lm", se = FALSE)
```

### correlation

```{r}
cor(data_RRS_noZero[, c("Rating", "Reviews", "Sales")])
```

The correlation between the number of reviews and the number of sales is the strongest, with a correlation coefficient of 0.665. This means that an increase in sales is likely due to an increase in the number of reviews. The correlation between the number of reviews and the drug rating is weak, with a correlation coefficient of 0.153. The correlation between the number of sales and the drug rating is also weak, with a correlation coefficient of 0.129. This indicates that drug rating may not have a significant impact on the increase in number of sales.

### Multiple Linear Regression

```{r}
model <- lm(Sales ~ Rating + Reviews, data = data_RRS_noZero)
summary(model)
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1), oma = c(0, 0, 2, 0))
plot(model)
```

Although the model only explains 44% of the variation in sales (R^2^ \> 0.7 indicates a good fit of the model), the linear regression model demonstrates that the impact of Reviews on sales is significant, whereas the impact of Rating on sales is not significant.

### Route Visualisation on a map

I used Cannabis as an example. It doesn't work well as NA, Unknown Location (I replaced it with NA), European Union, and World Wide cannot be shown on the map because they don't have coordinates (latitude and longitude) information. Please see the warning below. If I remove them, then in most cases, the drugs are shipped domestically, which is not useful to show them on the map. Therefore, I used Sankey Diagram to do the data visualisation without putting them on the map.

```{r}
#| warning: false
#replace "Unknown Location" with NA, Using Cannabis as an example
Route_Cannabis <- data %>% 
  filter(Drug_Type_L=="Cannabis") %>% 
  select(Ship_From, Ship_To) %>%
  mutate(Ship_To = str_replace(.$Ship_To, " - .*", "")) %>% 
    mutate(Ship_From = ifelse(Ship_From == "Unknown Location", NA, Ship_From), Ship_To = ifelse(Ship_To == "Unknown Location", NA, Ship_To)) %>% 
  group_by(Ship_From, Ship_To) %>%
  summarise(count = n()) %>%
  ungroup()
```

```{r}
#Convert the country names to ISO3 codes:
Route_Cannabis$iso_from <- countrycode(Route_Cannabis$Ship_From, "country.name", "iso3c")
Route_Cannabis$iso_to <- countrycode(Route_Cannabis$Ship_To, "country.name", "iso3c")


world <- ne_countries(scale = "medium", returnclass = "sf")
world$geometry <- st_make_valid(world$geometry)
coordinates <- data.frame(
  code = world$iso_a3,
  lon = as.numeric(st_coordinates(st_centroid(world$geometry))[, 1]),
  lat = as.numeric(st_coordinates(st_centroid(world$geometry))[, 2])
)


Route_Cannabis <- merge(Route_Cannabis, coordinates, by.x = "iso_from", by.y = "code")
Route_Cannabis <- merge(Route_Cannabis, coordinates, by.x = "iso_to", by.y = "code", suffixes = c("_from", "_to"))


#Calculate the midpoints and angles for the labels:
Route_Cannabis$mid_lat <- (Route_Cannabis$lat_from + Route_Cannabis$lat_to) / 2
Route_Cannabis$mid_lon <- (Route_Cannabis$lon_from + Route_Cannabis$lon_to) / 2
Route_Cannabis$angle <- with(Route_Cannabis, atan2(lat_to - lat_from, lon_to - lon_from) * 180 / pi)

map <- ggplot() +
  borders("world", colour = "gray50", fill = "gray80") +
  coord_fixed(xlim = c(-180, 180), ylim = c(-60, 90), ratio = 1.3) +
  theme_minimal() +
  theme(panel.grid = element_blank())

map + 
  geom_text(
    data = Route_Cannabis,
    aes(x = mid_lon, y = mid_lat, label = paste(Ship_From, "→", Ship_To), angle = angle, col='red'),
    size = 2,
    hjust = 0,
    vjust = 0,
    nudge_x = 0.5,
    nudge_y = 0.5
  )

```

### Sankey Diagram: Routes for Cannabis (interactive)

```{r}
#| warning: false
routes_type <- data %>%
  select(Ship_From, Ship_To, Drug_Type_L) %>% 
  group_by(Drug_Type_L,Ship_From, Ship_To) %>%
  summarise(count = n()) %>%
  arrange(Drug_Type_L, desc(count)) 

df <- routes_type %>%
  filter(Drug_Type_L == "Cannabis") %>% 
  select(Ship_From,Ship_To,count)  
   

nodes <- data.frame(name=c(df$Ship_From, df$Ship_To)) %>% unique()
  
df$IDsource=match(df$Ship_From, nodes$name)-1 
df$IDtarget=match(df$Ship_To, nodes$name)-1

ColourScal ='d3.scaleOrdinal() .range(["#FDE725FF","#B4DE2CFF","#6DCD59FF","#35B779FF","#1F9E89FF","#26828EFF","#31688EFF","#3E4A89FF","#482878FF","#440154FF"])'

sankeyNetwork(Links = df, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "count", NodeID = "name", 
              sinksRight=TRUE, colourScale=ColourScal, nodeWidth=60, fontSize=20, nodePadding=20)

```

Again, I used Cannabis as an example. If you hover your mouse over the gray band, you can see the frequency of appearances of this transportation route in all drug-related advertisements. The wider the gray band, the more frequent the occurrence of this route. You can also move the blocks around if the words overlap. We can substitute Cannabis with other types of drugs and compare the differences. However, due to space limitations, we may not be able to include all the necessary diagrams in our publication. So, the following way of data visualisation might be more helpful.

### Top 5 routes for each type of drug based on the number of advertisements

```{r}
#| warning: false
routes_type_top5 <- data %>%
  select(Ship_From, Ship_To, Drug_Type_L) %>% 
  group_by(Drug_Type_L, Ship_From, Ship_To) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(Drug_Type_L, desc(count)) %>% 
  group_by(Drug_Type_L) %>% 
  slice_head(n = 5) %>% 
  mutate(Route = paste(Ship_From, "→", Ship_To)) %>% 
  select(-Ship_From, -Ship_To) %>%
  mutate(Route = reorder_within(Route, count, Drug_Type_L))


ggplot(routes_type_top5, aes(x = count, y = Route, fill = Drug_Type_L)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  geom_text(aes(label = count), size = 2.5, position = position_dodge(width = 0.9), hjust = -0.1, vjust = 0.5) +
  labs(x = "Count", y = "Route", fill = "Drug Type") + 
  scale_fill_discrete(name = "Drug Type") + 
  scale_y_reordered() + 
  theme_minimal() + 
  theme(legend.position = "right", axis.text.y = element_text(angle = 0, hjust = 1, vjust = 0.5))

```

This diagram presents observations regarding the sending and destination locations for various drug types. The findings are as follows:

-   **Benzodiazepines (Benzos):** This drug type is primarily dispatched from the United States and the United Kingdom. The majority of shipments remain within their respective regions, while others are distributed globally.

-   **Cannabis:** Cannabis is predominantly sent from the United Kingdom, the United States, and Spain. Within the United Kingdom, there is significant domestic circulation, whereas the United States mainly receives shipments for its own region.

-   **Dissociatives and Opioids:** These two drug types are mainly dispatched from the United Kingdom, Netherlands, and the United States. They are distributed worldwide, although a portion is also sent to the sender's own region, either the United Kingdom or the United States.

-   **Ecstasy:** Ecstasy is shipped worldwide, with the Netherlands serving as the primary sending location. The circulation volumes in the United Kingdom and the United States are relatively smaller.

-   **Prescription Drugs:** The diagram indicates that India is the leading sending location for prescription drugs, followed by Germany and the Netherlands. These drugs are sent to various destinations worldwide, including the European Union, the United States, and the United Kingdom.

-   **Psychedelics:** The diagram suggests that the United States is the primary sending location for psychedelics, followed by the Netherlands. The destinations for psychedelics encompass the United States, the United Kingdom, and other global locations.

-   **Steroids:** The majority of steroids originate from an undisclosed location, while the United Kingdom also plays a role in their distribution.

-   **Stimulants:** The data reveals that the United States is the primary sending location for stimulants, followed by the Netherlands and Germany. These drugs are dispatched to various destinations worldwide, including the United States, the United Kingdom, and other locations.

-   **Weight Loss:** Based on the available data, weight loss drugs are shipped from Poland.

In summary, the sending and destination locations vary for different drug types. Some drugs circulate primarily within specific regions, while others have a global circulation. However, the distribution of vendors appears to be concentrated within the UK and EU regions, with sporadic presence of US-based vendors. These insights can help us understand the circulation trends and market demand for different drug types.

### 

## Limitations

The data sample size is limited, and the time frame for data collection spans 11 days. However, trading was ongoing during this period, and variables such as ratings, the number of sales and reviews were constantly changing. These changes could impact the statistical data and comparisons. The sales data collected on day 1 from one vendor may differ significantly from the data collected from another vendor on day 11. However, if both sets of data were collected on the same day, the differences in sales data might not be as significant.
